# Introduction {#intro}

In this section, we'll start with some basic concepts of web development and then introduce Shiny by explaining the advantages of Shiny and how it works. At last we'll give a list of useful resources in learning Shiny.

## Web development

Here are some concepts that usually used in web development. Knowing them might make you look like more professional:)

**Static web page**

> A static web page (sometimes called a flat page/stationary page) is a web page that is delivered to the user exactly as stored. (from [wiki](https://en.wikipedia.org/wiki/Static_web_page))

```{r static-page, fig.cap='Static web page: is delivered to the user exactly as stored.', echo=FALSE}
knitr::include_graphics('imgs/Scheme_static_page_en.svg')
```

**Dynamic web page**

> A server-side dynamic web page is a web page whose construction is controlled by an application server processing server-side scripts. (from [wiki](https://en.wikipedia.org/wiki/Dynamic_web_page))

```{r dynamic-page, fig.cap='Dynamic web page: example of server-side scripting (PHP and MySQL).', echo=FALSE}
knitr::include_graphics('imgs/Scheme_dynamic_page_en.svg')
```

**Web application** 

> A Web application (Web app) is an application program that is stored on a remote server and delivered over the Internet through a browser interface. (from [WhatIs.com](searchsoftwarequality.techtarget.com/definition/Web-application-Web-app))


**Web (application) framework** 

> A Web framework is a collection of packages or modules which allow developers to write Web applications or services without having to handle such low-level details as protocols, sockets or process/thread management. (from [PythonWiki](https://wiki.python.org/moin/WebFrameworks))

**Front-end web development** 

> Front-end web development, also known as client-side development is the practice of producing HTML, CSS and JavaScript for a website or web application so that a user can see and interact with them directly. (from [Wiki](https://en.wikipedia.org/wiki/Front-end_web_development))

**Back-end web development** 

> Back-end web development creates the logical back-end and core computational logic of a website. (from [techopedia](https://www.techopedia.com/definition/29568/back-end-developer))

## Shiny

[Shiny](http://shiny.rstudio.com/)  is a web application framework for R that can help turn your analyses into interactive web applications.

- No HTML, CSS, or JavaScript knowledge required

**Why Shiny?**

- Easy to learn, easy to use.
- The development time is minimized.
- Excellent tool for data visualization.
- Have very strong backing: the R language
- Fun & Cool.

A **Shiny app** usually contains two parts:

1. UI: controls the outlook of the web page
2. Server: (a live R session) controls the logic

**How does Shiny app work?**

The "Server" keeps monitoring the UI. Whenever there is a change in the UI, the "Server" will follow some instructions (run some R code) accordingly and update the UI's display. (This is the basic idea of **reactive** expression, which is an distinguish feature of Shiny we will talk about later.)

**Example**

```{r eg1, eval=FALSE}
library(shiny)
runExample("01_hello") # a histogram
```

In the example above, the "Server" keeps monitoring the "slider" in the page, and whenever there is a change with it, the "Server" will re-execute a block of R code to regenerate the hitogram.

## Resources

1. Shiny portal site: <http://shiny.rstudio.com>
    - Tutorial (get started): <http://shiny.rstudio.com/tutorial/>
    - Articles (go deeper): <http://shiny.rstudio.com/articles/>
    - Gallery (get inspired): <http://shiny.rstudio.com/gallery/>
2. Shiny User Showcase: <https://www.rstudio.com/products/shiny/shiny-user-showcase/>
    - Shiny Apps for the Enterprise
    - Industry Specific Shiny Apps
    - Shiny Apps as Analytics Tools
    - Shiny Apps that Extend Shiny
    - Shiny Apps with Popular Appeal
    - Shiny Apps for Teaching
3. Shiny examples (over 100 examples): <https://github.com/rstudio/shiny-examples>
4. Ask questions in the shiny google group: <https://groups.google.com/forum/#!forum/shiny-discuss>
5. Articles from R blogger: <http://www.r-bloggers.com/?s=shiny>
6. Gallery of user-made apps: <http://www.showmeshiny.com/>
7. 2016 Shiny Developer Conference Videos <https://www.rstudio.com/resources/webinars/shiny-developer-conference/>

