--- 
title: "Shiny Tutorial"
author: "Weicheng Zhu"
date: "`r Sys.Date()`"
knit: "bookdown::render_book"
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
site: bookdown::bookdown_site
description: "This is a shiny tutorial."
---


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
knitr::opts_chunk$set(fig.align='center')
```


# Prerequisites

This tutorial is designed for Shiny beginner. You don't need any background in the [`R`](https://www.r-project.org/) language or `Shiny` to get started, although having some basic knowlege about `R` might be helpful.

It would be helpful if you have some basic knowlege about `HTML`, `CSS` and `javascript`, but they are not required too.

## Softwares
- [R](https://www.r-project.org/) (required). Better to use the latest version of R (3.3.0 for the time this tutorial is written).
- The `shiny` package (required). To install the package from CRAN by using:

```{r, eval=FALSE}
install.packages("shiny")
```
- [Rstudio](https://www.rstudio.com/products/rstudio/download/) (recommended). A user friendly IDE for R. Very convenient tool in building shiny apps.
- A web browser. Better to use Google chrome or Firefox.

